\herschel\footnote{{\it Herschel} is an ESA space observatory with science instruments provided by European-led Principal Investigator consortia and with important participation from NASA.} Orion Protostar Survey (HOPS) Imaging and Photometry Results.

### 2017-04-24 HOPS/photometry/ms.tex
update to ms

A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Thus, a primary goal of current Galactic star-formation research is to develop such a comprehensive theory of star formation. However, many details and key ingredients needed to complete our picture of the star-formation process are not well understood \citep{mo07}.  In particular, one critical aspect, the connection between the raw materials and the final product (the star) is not well characterized \citep{dunham}.  In other words, while the building blocks and the conditions for the formation of stars are provided by the underlying environment, the influence of these building blocks on the subsequent population is not understood.  The importance of star-formation is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.

@@

Unfortunately, this link to their environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  And, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy. 

@@

To properly remove the degeneracies from (i), we require sufficient spatial resolution and multi-wavelength measurements to disentangle the various components that make up the protostar and its environment.  We also require sufficiently large number of protostars in a diverse set of environmental conditions to .  to properly tackle (i), the degeneracies between the protostar and its environment.  These requirements limit the best candidate we chose to study a large number of protostars.  Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer.  At 419 pc, Orion is relatively nearby \citep{schlafly} and, thus, allows excellent spatial resolution.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}.

@@

\spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is the defining characteristic of a protostar. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light in those wavelengths.

@@

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  All 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 409 sources in the final sample included here.  Note that \cite{furlan}\ also include one additional source from \cite{tobin}\ which was not available when the analysis for this work was completed.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, \cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 409 objects in this contribution.

@@

\par
\subsection{Flux distribution functions}
\label{lfs}
\par
Figure~\ref{fig:fd}\ shows the flux distribution (FD) functions at 70~\micron\ and 160~\micron, respectively, for all 409 sources detected in our sample.  Figures~\ref{fig:fd70regional}~\&~\ref{fig:fd160regional} show the flux distributions segregated by sub-region, and separately for the Orion~A (left column) and Orion~B (right column) clouds.  The sub-region and the number of associated sources are identified within the sub-panels of the Figures.  We do not consider upper limits in these FDs (sources with flag value = 2 in Table~\ref{tbl:obs}). There are distinct differences apparent in the observed flux distributions as a function of sub-region.  We note that in a flux-limited survey, such as ours, local environmental differences in the amount and structure of the nebular emission can significantly bias source detection and photometry algorithms.  We quantify FD differences and investigate the role of bias below.
\par
The 70~\micron\ FDs are relatively flat (\ie, the number of sources in all bins is similar) for the Orion~B sub-regions: LDN~1622, NGC~2068, and NGC~2023/4.  This situation is likely due to the low numbers of protostars available for each sub-region.  In Orion~A, the 70~\micron\ FDs have an apparent peak at or near 1 Jy in all sub-regions.  And, no significant differences are obvious between sub-regions, except for LDN~1641-N.
\par
The 160~\micron\ FDs show clear and obvious differences amongst the sub-regions.  The following results, in particular, are noted: (i) there is a complete lack of sources below $\sim$500~mJy in OMC-2/3 region.  (ii) The LDN~1641 (all) and OMC~2/3 sub-regions have apparent peaks in FDs at different flux values.  (iii) The peak of the ONC-S flux distribution is between those of LDN~1641 and OMC~2/3.  And, (iv) in Orion~B, LDN~1622 and NGC~2023/4 show differences in the observed distribution, even with the low number of sources available.
\par
The 160~\micron\ FDs suggest a trend of increasingly bright sources towards lower declinations in Orion~B, and increasingly bright sources towards higher declinations in Orion~A.  We investigate this apparent trend by plotting the median flux for each sub region as a function of declination.  Figure~\ref{fig:mdFlux_v_dec} shows the resulting quantitative correlations.  The median shows a systematic change as a function of declination (sub-region) as noted above.  The trend is, however, weakly noted in the 70~\micron\ fluxes, and shows OMC 2/3 region with significantly different median flux for the 160~\micron\ fluxes.  The implications for this result are discussed in Section~\ref{sec:discussion}.

@@

\bibitem[Dunham \etal\ (2014)]{dunham} Dunham, M. M., Stutz, A. M., Allen, L. E., Evans, N. J., II, Fischer, W. J., Megeath, S. T., Myers, P. C., Offner, S. S. R., Poteet, C. A., Tobin, J. J. \& Vorobyov, E. I.in Protostars and Planets VI, Henrik Beuther, Ralf S. Klessen, Cornelis P. Dullemond, and Thomas Henning (eds.), University of Arizona Press, Tucson, pp.195-218

>>>>

A comprehensive theory of the formation of stars, which explains the origins of stars from the local raw materials and environmental conditions, is necessary for understanding processes spanning the entire range of cosmic evolution from the formation and evolution of galaxies to the formation of planets \citep{ke2012}.  Thus, a primary goal of current Galactic star-formation research is to develop such a comprehensive narrative of star formation. However, many details and key ingredients needed to complete our picture of the star-formation process are not well understood \citep{mo07}.  In particular, one critical aspect, the connection between the raw materials and the final product (the star) is not well characterized \citep{dunham}.  In other words, while the building blocks and the conditions for the formation of stars are provided by the underlying environment, the influence of these building blocks on the subsequent population is not understood.  The importance of star-formation is further underscored by the expansive open and guaranteed-time legacy-class observing programs scheduled on major space-based observatories \spitzer\ \citep{spitzer}, and \herschel\ \footnote{In fact, the former name of \herschel, FIRST was an homage to one of primary objectives of \herschel: the study of the first stars and galaxies in their earliest stages.} \citep{herschel}.

@@

Unfortunately, this strong link to their surrounding environment also makes protostars difficult to study.  In particular:  (i) observational studies must be able to disentangle the degenerate effects of both the environment and the star-formation process itself.  And, (ii) the presence of dust in the local environment means the amount of extinction in lines-of-sight to star formation regions is abnormally high (few to several tens of magnitudes in the visual) compared to most of the rest of the Galaxy \citep{dobbs}.

@@

To properly remove the degeneracies from (i), we require sufficient spatial resolution and multi-wavelength measurements to disentangle the emission and morphology of the various components that make up the protostar and its immediate environ.  We also require sufficiently large number of protostars in a diverse set of environmental conditions to properly investigate the role of initial conditions on the fundamental properties of the emergent star.  Further, the effects of extinction (ii, above) and the required sensitivity to detect and study a large sample of protostars is mitigated by using focusing on infrared and longer wavelengths.  The extinction at infrared and radio wavelengths is orders of magnitude lower than at optical \citep{extinction}.

@@

Besides alleviating interstellar extinction, \spitzer\ and \herschel\ observations, in particular, confirmed long recognized views that far-IR observations of the reprocessed radiation can probe the evolution of protostars \citep{als87}.  The presence of an infalling envelope of gas and dust is the defining characteristic of a protostar. This envelope absorbs the radiation from the central accreting star+disk and reprocesses most of the luminosity into the far-IR \citep{ali}.   Far-IR observations are, therefore, absolutely crucial for efficiently identifying and studying protostars because protostars emit most of their light at those wavelengths.
The combination of the nearby Orion star-forming region and the near- to far-infrared capabilities of \herschel\ and \spitzer\ allow us to meet our main requirements (above).   Orion provides several key advantages.  \cite{orion} identified a rich sample of protostars in Orion from \spitzer\ thus providing us a collection of protostars in a variety of environmental conditions.  Star formation has been observed in a rich diversity of environments, from isolated cold globules to rich clusters. See, for example, \cite{carpenter}, \cite{feigelson}, \cite{amy2010}. At 419 pc \citep{schlafly} , Orion is relatively nearby and, thus, allows excellent spatial resolution with both \herschel\ and \spitzer.  

@@

\section{Protostar sample \& observations}
\label{sec:sample}
\par
The \spitzer\ Orion protostar sample was defined and described by \cite{orion}.  We selected a flux-limited subset of 280 protostars for follow-up with \herschel\  for HOPS.  The number of targets for the HOPS follow-up was limited solely by signal-to-noise ratio (S/N) considerations.  Our original sample of 280 \herschel\ targets were segregated in distinct spatial tiles to optimize observing.  The tiles were assigned consecutive three-digit integer group numbers starting with the number 0 (zero).  The spatial sizes of the tiles ranged from 3\arcmin\ (most common) to 7\arcmin).  The protostar candidates selected for our \herschel\ survey are referred to as the HOPS sources and are uniquely identified by a 3-digit integer number starting with the number 0 (zero).   Ultimately, we detected additional candidates previously identified in the \spitzer\ survey whose spatial location happened to be within the field-of-view of the observation tile.  These sources, however, were not part of the original HOPS candidate list because their estimated fluxes were below our S/N limit.  Further, \cite{pbrpaper} found protostars and candidates not identified in the \spitzer\ list; See section~\ref{sec:protostars} for more details.  Our final catalog appends the original sample of 280 targets with the additions mentioned above.  There are a total of 410 sources in the final sample included here.
\par
\cite{furlan}\ classified 330 of these sources as young stellar objects (YSOs) and the remaining as unlikely to be protostars and/or sources not observed or detected by PACS at 70~micron.  For their analysis, \cite{furlan} focus on the 330 HOPS targets which have complete \spitzer\ and \herschel\ data (at least a PACS 70~\micron\ detection) and most were originally considered protostars by \cite{orion}.  The objective of this contribution is to provide complete data on all sources from our original sample of 280 protostars as well as the additional targets detected in our images.  Thus, we have included all 410 objects in this contribution.

@@

\par
\subsection{Flux distribution functions}
\label{lfs}
\par
Figure~\ref{fig:fd}\ shows the flux distribution (FD) functions at 70~\micron\ and 160~\micron, respectively, for all sources detected in our sample.  Figures~\ref{fig:fd70regional}~\&~\ref{fig:fd160regional} show the flux distributions segregated by sub-region, and separately for the Orion~A (left column) and Orion~B (right column) clouds.  The sub-region and the number of associated sources are identified within the sub-panels of the Figures.  We do not consider upper limits in these FDs (sources with flag value = 2 in Table~\ref{tbl:obs}). There are distinct differences apparent in the observed flux distributions as a function of sub-region.  We note that in a flux-limited survey, such as ours, local environmental differences in the amount and structure of the nebular emission can significantly bias source detection and photometry algorithms.  We quantify FD differences and investigate the role of bias below.
\par
The 70~\micron\ FDs are relatively flat (\ie, the number of sources in all bins is similar) for the Orion~B sub-regions: LDN~1622, NGC~2068, and NGC~2023/4.  This situation is likely due to the low numbers of protostars available for each sub-region.  In Orion~A, the 70~\micron\ FDs have an apparent peak at or near 1 Jy in all sub-regions.  And, no significant differences are obvious between sub-regions, except for LDN~1641-N.
\par
The 160~\micron\ FDs show clear and obvious differences amongst the sub-regions.  The following results, in particular, are noted: (i) there is a complete lack of sources below $\sim$500~mJy in OMC-2/3 region.  (ii) The LDN~1641 (all) and OMC~2/3 sub-regions have apparent peaks in FDs at different flux values.  (iii) The peak of the ONC-S flux distribution is between those of LDN~1641 and OMC~2/3.  And, (iv) in Orion~B, LDN~1622 and NGC~2023/4 show differences in the observed distribution, even with the low number of sources available.
\par
The 160~\micron\ FDs suggest a trend of increasingly bright sources towards lower declinations in Orion~B, and increasingly bright sources towards higher declinations in Orion~A.  We investigate this apparent trend by plotting the median flux for each sub region as a function of declination.  Figure~\ref{fig:mdFlux_v_dec} shows the resulting quantitative correlations.  The median shows a systematic change as a function of declination (sub-region) as noted above.  The trend is, however, weakly noted in the 70~\micron\ fluxes, and shows OMC 2/3 region with significantly different median flux for the 160~\micron\ fluxes.  The implications for this result are discussed in Section~\ref{sec:discussion}.

@@

\bibitem[Dobbs \etal\ (2014)]{dobbs} Dobbs, C. L., Krumholz, M. R., Ballesteros-Paredes, J., Bolatto, A. D., Fukui, Y., Heyer, M., Low, M.-M. M., Ostriker, E. C., \& Vazquez-Semadeni, E. 2014, In {\it Protostars and Planets VI}, Henrik Beuther, Ralf S. Klessen, Cornelis  P. Dullemond, and Thomas Henning (eds.), University of Arizona Press, Tucson, pp. 3-26
\bibitem[Draine (2003)]{extinction} Draine, B. T., 2003, ARA\&A, 41, 241
\bibitem[Dunham \etal\ (2014)]{dunham} Dunham, M. M., Stutz, A. M., Allen, L. E., Evans, N. J., II, Fischer, W. J., Megeath, S. T., Myers, P. C., Offner, S. S. R., Poteet, C. A., Tobin, J. J. \& Vorobyov, E. I. in {\it Protostars and Planets VI}, Henrik Beuther, Ralf S. Klessen, Cornelis P. Dullemond, and Thomas Henning (eds.), University of Arizona Press, Tucson, pp.195-218
